\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix typo
Let's not fix ourselves on "random" here. There are good reasons to choose distributers non-randomly, but we haven't worked out the details yet what we want to do.

A normal downloading flow goes as follows \footnote{This is a highly information description which will be fleshed out in future drafts.}.

@@

If so, then a session is added to the session registry, which is in the started state and where the distributor has been randomly chosen among the available ready set.

>>>>

A normal downloading flow goes as follows \footnote{This is a highly informal description which will be fleshed out in future drafts.}.

@@

If so, then a session is added to the session registry, which is in the started state and where the distributor has been chosen from the available ready set.
